Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-06-27 Response.tex

\item 
    \begin{itshape}
"It has been shown that there exist multi-dimensional tubes, or invariant manifolds, of constant energy trajectories that span the state space."  The "tube" statement is really only true for some libration point orbits at certain Jacobi Constants.  For some orbits these structures are more chaotic and don't resemble tubes.  May want to soften this language or change "tubes" to "structures".
\end{itshape}

The sentence has been modified as follows.

\begin{correction}
It has been shown that there exist multi-dimensional structures, termed invariant manifolds, of constant energy trajectories that span the state space. 
\end{correction}

\item 
    \begin{itshape}
-"In this paper, we propose a systematic design method which enables low-thrust transfers in the planar circular restricted three-body problem." Why planar?  For simplicity?  Almost all parking orbits departing the Earth are likely going to have some inclination with respect to the rotating reference plane, and will likely require some three-dimensional thrusting to target the manifold.  You may want to indicate that this is a first step in the research to exploit the Poincare sections more easily, which is why I'm assuming it was done.  It doesn't hurt to be straightforward about this, as it is a first-step towards characterizing the design space.
\end{itshape}

The introduction has been modified with an additional sentence indicating our use of the planar three body problem

\begin{correction}
Utilizing the planar assumption greatly simplifies the problem and allows for the use of established methods in determining periodic orbits and \Poincare sections.
\end{correction}

\item 
    \begin{itshape}
-"In addition, through the use of geometric integrators we accurately capture the effects of low thrust on the system dynamics in the numerical simulation."  A variational integrator will accurately capture the qualitative effects of the transfer (e.g. propellant use), however it will not necessarily accurately capture accuracy in the final state vector - it is guaranteed to be on an energy surface, but it is not guaranteed to be at exactly the right location on the energy surface.  I would soften this claim or reword.
\end{itshape}

While the geometric integrator will not exactly characterize the terminal energy or state of a dynamic system, it will better preserve the total energy variation as compared to convential integration schemes. 
In addition, the total energy deviation will remain bounded and less than than of convential schemes which experience unbounded energy deviation. 
As a result, the terminal state/energy will be more accurately characterized using a variational integrator as compared to conventional schemes. 
Also this difference becomes more evident over increasing time horizons.
Some additional detail has been added stating that the increased accuracy is most evident over long time periods.

\begin{correction}
In addition, through the use of geometric integrators we more accurately capture the effects of low thrust on the system dynamics in the numerical simulation over extended periods which are typical of electric propulsion systems. 
\end{correction}
-"The Poincare section reduces the dimensionality of the system dyanmics to the study of a related discrete update map." It does, but at the expense if a large up-front computational run that must be run well in advance to capture the problem characteristics.  Also, it is more challenging to execute in 3D, which should be noted.

### 2017-06-27 manuscript.tex
Reword another paragraph summarizing key idea
Reviewer 1 Comment 7 and Comment 8

>>>>

%-------------------- OBJECTIVES OF THIS WORK-----------------------------%
% SYSTEMATIC DESIGN TO AVOID DIFFICULTIES IN CHOOSING A GOOD INITIAL GUESS
% CAPTURE LONG TERM EFFECTS OF LOW THRUST ACCURATELY IN NUMERICAL SIMULATION
In this paper, we propose a systematic design method which enables low-thrust transfers in the planar circular restricted three-body problem.
Utilizing the planar assumption greatly simplifies the problem and allows for the use of established methods in determining periodic orbits and \Poincare~sections.
We utilize the concept of the reachability set to enable a simple methodology of selecting initial conditions to achieve general orbital transfers. 
Through the use of a simple distance metric on a \Poincare~section greatly reduces the dimensionality of the reachability analysis and provides an approximation of the reachability set.
In addition, through the use of geometric integrators we more accurately capture the effects of low thrust on the system dynamics in the numerical simulation over extended periods which are typical of electric propulsion systems. 
With this proposed method, the previous research on control-free trajectories will be generalized with the addition of low thrust propulsion systems.
